Automated discovery of interpretable gravitational-wave population models

### 2022-07-10 src/tex/ms.tex
Reformat methods

Next, given the set of the best expressions at each complexity $\mathcal{S}^\ast = \{s_c\}_{c\in\{1,\ldots,80\}}$,
we can define the \textit{score} of an expression as the slope of the accuracy-complexity curve, equal to:
\begin{equation}
    \text{score} = -\frac{\Delta (\log \mathcal{L}(s))}{\Delta(\abs{s})},
\end{equation}
which is a heuristic for the quality of a particular equation, used in the symbolic regression literature \cite{eureqa,cranmerDiscoveringSymbolicModels2020}.
Finally, we can construct the \textit{Pareto curve}, defined as:
\begin{equation}
    \hat{\mathcal{S}}^\ast = \{s_c \ |\ \mathcal{L}(s_c) < \mathcal{L}(s_q) \forall c > q \},
\end{equation}
such that each remaining expression is more accurate than all simpler expressions.

>>>>

Next, given the set of the best expressions at each complexity $\mathcal{S}^\ast = \{s_c\}_{c\in\{1,\ldots,80\}}$,
Next, we can construct the \textit{Pareto curve}, defined as:
\begin{equation}
    \hat{\mathcal{S}}^\ast = \{s_c \ |\ \mathcal{L}(s_c) < \mathcal{L}(s_q) \forall c > q \},
\end{equation}
such that each remaining expression is more accurate than all simpler expressions.
Using this, we can define the \textit{score} of an expression as the slope of the Pareto curve, equal to:
\begin{equation}
    \text{score} = \frac{\Delta (-\log \mathcal{L}(s))}{\Delta(\abs{s})},
\end{equation}
which is a heuristic for the quality of a particular equation, used in the symbolic regression literature \cite{eureqa,cranmerDiscoveringSymbolicModels2020}.
